---
title: "The QM 2020 Interactive Student Collage"
output:
  github_document
always_allow_html: true
---

```{r, include=FALSE}
library(shiny)
```

[Denis Cohen](https://twitter.com/denis_cohen), [Marcel Neunhoeffer](https://twitter.com/mneunho) & [Oliver Rittmann](https://www.sowi.uni-mannheim.de/gschwend/team/postdocs-and-doctoral-students/oliver-rittmann/)

# Facilitating Social Interactions During the Online Semester

The COVID-19 pandemic has forced universities around the globe to switch from
on-site teaching to online teaching. This comes with various challenges.

One the one hand, online teaching makes it **harder for instructors to get to know their students**.
To alleviate this problem, we asked our students to fill out this [short questionnaire](https://github.com/SocialScienceDataLab/denis-cohen/blob/main/QM 2020 Survey.pdf) on our course page on the learning management system ILIAS and to attend our virtual office hours regularly.

On the other hand, online teaching also makes it **harder for students to get to know each other** and to forge bonds for mutual academic and personal support.
To alleviate this problem, we developed as twofold strategy.
At the beginning of the semester, we asked students for their consent that we use some basic information (name, current and previous programs of study, academic interests, and profile pictures) from the ILIAS survey to compose an interactive student collage and share it with the class. Specifically, we developed a ShinyApp, based on the [shinysense::shinywipr](https://github.com/nstrayer/shinysense) module. This tool allowed participants to get to know each other and to find mutual interests with their fellow students in a fun and interactive way by swiping through fellow students profiles. This GitHub repository contains the [questionnaire](https://github.com/SocialScienceDataLab/denis-cohen/blob/main/QM 2020 Survey.pdf) for our ILIAS Survey, code for data processing and the soruce code of our ShinyApp. A demo of the App can be found on [shinyapps.io](https://denis-cohen.shinyapps.io/collage_app/). Our guide for the local installation of the App can be found in the [Getting Started](#getting-started) section below.

We followed up on this with two virtual social events in Weeks 4 and 8 of the semester that allowed students to mingle in an informal setting in Zoom Breakout Rooms. Additionally, we encouraged students to actively help each other in the student forum on ILIAS and fostered mutual support systems by assigning weekly exercise that had to be completed collaboratively, where groups changed every three weeks.


# Getting Started

Time to get to know your fellow students! Based on the info you provided on the ILIAS survey, we have compiled an interactive student collage for you. 

Instead of having you scroll through a long PDF document with 40+ student profiles as in a yearbook, we have developed a [ShinyApp](https://www.shinyapps.io/) that allows you to actively engage with each profile by swiping through them. 

## How to Run the App

### Step 1: Packages

To run the ShinyApp on your computer, you first need to install and load some packages, using the following code:

```{r, eval = FALSE}
## ---- Packages ----
## Packages
pkgs <- c("devtools",
          "shiny",
          "dplyr")

## Install uninstalled packages
lapply(pkgs[!(pkgs %in% installed.packages())],
       install.packages,
       repos = "http://cran.us.r-project.org")

## Load all packages to library and adjust options
lapply(pkgs, library, character.only = TRUE)

## shinyswipr
if (!("shinysense" %in% installed.packages()))
  devtools::install_github("nstrayer/shinysense")
library(shinysense)
```

### Step 2: Downloading and Running the App

Next, download the `collage_app.zip` from ILIAS and save it to a folder of your choosing. Save the path to the file as an R object `zip_file`. Note that when using Windows, you must either replace the back slashes (`\`) in the path with forward slashes (`/`) or double back slashes (`\\`).

```{r, eval=FALSE}
zip_file <- "/folder/for/my/download/collage_app.zip"
```

Then, specify a path to a folder where you would like to unpack the app and save it in the object `out_dir`.

```{r, eval=FALSE}
out_dir <- "/folder/to/unpack/collage_app"
```

You can then unpack and run the app by submitting these three commands:

```{r, eval=FALSE}
unzip(zip_file, exdir = out_dir)
setwd(out_dir)
shiny::runApp("collage_app")
```

### Step 3: Using the App

You can then use the app by swiping through the profiles. You can:

  `r icon("hand-point-left")` Swipe left if you share academic interests with a fellow student.
  
  `r icon("hand-point-right")` Swipe right if you would like to chat about their current or previous programs.
  
  `r icon("hand-point-up")` Swipe up if both apply...
  
  `r icon("hand-point-down")` ...and down if neither apply.
  
You can either swipe by using drag and drop (i.e., clicking on each profile and moving it to one of the four directions before releasing the mouse button) or using your finger if your device has a touch screen.
  
Note that this app runs locally on your computer. It does not send or upload any data, so neither we nor any of your fellow students will know how you swiped. It is interactive in the sense that you can interact with the app; it does not allow you to interact with other students.

The app shows you a table with your swiping history for your convernience. You can, of course, save your own swiping history and use it to decide whom to talk to at our upcoming social event.

## Selection Rules

We have included profiles of students who **completed and submitted** the survey on ILIAS (or emailed us that they forgot to submit their completed survey) *and* agreed that at least their **name** be used for the student collage. Out of this subset, we have included **pictures** if students agreed to the use of their pictures for the collage *and* **uploaded** a profile picture. Lastly, we only included information on academic interest and current and previous programs of study if students agreed to the use of this information for the collage.

## Links

Interested in developing your own ShinyApp? Check out this [Methods Bites Tutorial](https://www.mzes.uni-mannheim.de/socialsciencedatalab/article/shiny-apps/) by [Konstantin Gavras](https://twitter.com/kongavras) and [Nick Baumann](https://twitter.com/Nick_Baumann97)!
